|

### 2023-01-22 paper_comparison/paper_comparison/paper_comparison.Rmd
modify the different observations plot

# Generate data for 300 observations
ori_dat <- poly_model(shape = 2, 
                      x = {
                        raw_x <- rand_uniform(-1, 1);
                        closed_form(~stand_dist(raw_x))
                        }, 
                      sigma = 1.5)$gen(300)

# Plot data for 300 observations
np300 <- VI_MODEL$plot(ori_dat) + 
  ggtitle(quote(n~"="~300)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for 50 observations
np50 <- poly_model(shape = 2, 
                   x = {
                     raw_x <- rand_uniform(-1, 1);
                     closed_form(~stand_dist(raw_x))
                     }, 
                   sigma = 1.5)$
  gen(50, computed = select(ori_dat[1:50, ], x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(n~"="~50)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for 100 observations
np100 <- poly_model(shape = 2, 
                    x = {
                      raw_x <- rand_uniform(-1, 1);
                      closed_form(~stand_dist(raw_x))
                      }, 
                    sigma = 1.5)$
  gen(50, computed = select(ori_dat[1:100,], x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(n~"="~100)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

patchwork::wrap_plots(np50, np100, np300, ncol = 3)
```

>>>>

# Generate data for 300 observations
dat_n_300 <- poly_model(shape = 2, 
                        x = {
                          raw_x <- rand_uniform(-1, 1);
                          closed_form(~stand_dist(raw_x))
                        },
                        sigma = 1.5)$gen(300) %>%
  mutate(n = "N = 300")

# Generate data for other settings
map(c(50, 100), function(n) {
  poly_model(shape = 2, 
                   x = {
                     raw_x <- rand_uniform(-1, 1);
                     closed_form(~stand_dist(raw_x))
                     }, 
             sigma = 1.5)$
    gen(n, computed = select(dat_n_300[1:n, ], x, e)) %>%
    mutate(n = paste0("N = ", n))
}) %>%
  bind_rows(dat_n_300) %>%
  VI_MODEL$plot() +
  theme_light() +
  facet_wrap(~n, scales = "free", ncol = 3) +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```
